Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-24 appendix.tex
tex

\begin{enumerate}[noitemsep]
	\item Only aap in ICS?
	\item Why not aa~p~ in ICS?
	\item Have you tried FAT?
	\item What if we mix HM(RM) and HM(SM)?
	\item Another example for the GA pseudo-hardness function family?
	\item Why not ResNet-50?
\end{enumerate}

>>>>

\begin{enumerate}[noitemsep, label={Q.{\arabic*}}]
		%
	\item {\it There is only $L_\text{T}(\va, \tilde{\va}, \vp)$ in the ICS
		term.  Is it possible to introduce any other triplet combinations among
		the six samples (\ie, three benign and three adversarial)?}\\
		%
		A: We have tried some other combinations, and they are either not
		effective, or causing negative effects.
		%
		In particular, adding $L_\text{T}(\va, \vp, \vn)$ on top of the
		adversarial training loss
		$L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn})$ can improve
		performance on benign examples, but will drastically reduce model
		robustness.

	\item Why not aa~p~ in ICS?
		less adversarial, further.
	\item Have you tried FAT?
	\item What if we mix HM(RM) and HM(SM)?
	\item Another example for the GA pseudo-hardness function family?
	\item Why not ResNet-50?
\end{enumerate}
